### 2023-01-24 Poisot_et_al_2023_ncbitaxonomyjl__draft.tex
Deploying to gh-pages from @ PoisotLab/ms_ncbitaxonomy_softwarenote@aabfcbf2552d76846f10d88446d3cdc8f18de681 🚀

@@

\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc} % for \widthof, \maxof
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\maxof{\widthof{#1}}{\csllabelwidth}}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth}{#1}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}\geometry{verbose,letterpaper,tmargin=2.2cm,bmargin=2.2cm,lmargin=2.2cm,rmargin=2.2cm}

@@

%
\href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
%
\,\textsuperscript{1,2}\quad %
\href{https://orcid.org/0000-0002-0965-1649}{Rory\,Gibb}%
%
\,\textsuperscript{3,4,5}\quad %
\href{https://orcid.org/0000-0002-4308-6321}{Sadie J.\,Ryan}%
%
\,\textsuperscript{6,7,8}\quad %
\href{https://orcid.org/0000-0001-6960-8434}{Colin J.\,Carlson}%
%
\,\textsuperscript{9,10}

\textsuperscript{1}\,Université de Montréal, Départment de Sciences
Biologiques, Montréal QC, Canada\quad \textsuperscript{2}\,Québec Centre
for Biodiversity Science, Montréal, QC,
Canada\quad \textsuperscript{3}\,Centre on Climate Change and Planetary
Health, London School of Hygiene and Tropical Medicine, London,
UK\quad \textsuperscript{4}\,Centre for Mathematical Modelling of
Infectious Diseases, London School of Hygiene and Tropical Medicine,
London, UK\quad \textsuperscript{5}\,Current address: Centre for
Biodiversity and Environment Research, University College London,
London, UK\quad \textsuperscript{6}\,Emerging Pathogens Institute,
University of Florida, Gainesville, FL, United States of
America\quad \textsuperscript{7}\,School of Life Sciences, University of
KwaZulu-Natal, Durban, South Africa\quad \textsuperscript{8}\,Department
of Geography, University of Florida, Gainesville, FL, United States of
America\quad \textsuperscript{9}\,Department of Microbiology and
Immunology, Georgetown University Medical Center, Georgetown University,
Washington, D.C., United States of
America\quad \textsuperscript{10}\,Center for Global Health Science and
Security, Georgetown University Medical Center, Georgetown University,
Washington, D.C., United States of America

@@

@@

\vfill
\texttt{NCBITaxonomy.jl} is a package designed to facilitate the
reconciliation and cleaning of taxonomic names, using a local copy of
the NCBI taxonomic backbone (Federhen 2012, Schoch et al. 2020); The
basic search functions are coupled with quality-of-life functions
including case-insensitive search and custom fuzzy string matching to
facilitate the amount of information that can be extracted automatically
while allowing efficient manual curation and inspection of results.
\texttt{NCBITaxonomy.jl} works with version 1.6 of the Julia programming
language (Bezanson et al. 2017), and relies on the Apache Arrow format
to store a local copy of the NCBI raw taxonomy files. The design of
\texttt{NCBITaxonomy.jl} has been inspired by similar efforts, like the
R package \texttt{taxadb} (Norman et al. 2020), which provides an
offline alternative to packages like \texttt{taxize} (Chamberlain and
Szöcs 2013).

@@

Unambiguously identifying species is a far more challenging task than it
may appear. There are a vast number of reasons for this. Different
databases keep different taxonomic ``backbones,'' \emph{i.e.} different
data structures in which names are mapped to species, and organised in a
hierarchy. Not all names are unique identifiers to groups. For example,
\emph{Io} can either refer to a genus of plants from the aster family,
or to a genus of molluscs; the genus \emph{Mus} (of which the house
mouse \emph{Mus musculus} is a species), contains a sub-genus
\emph{also} named \emph{Mus} (within which \emph{Mus musculus} is
located). Conversely, the same species can have several names, which are
valid synonyms: for example, the domestic cow \emph{Bos taurus} admits
\emph{Bos primigenius taurus} as a valid synonym. In addition to
binomial names, the same species can be known by many vernacular
(common) names, which are language or even region-specific: \emph{Ovis
aries}, for example, has valid English vernaculars including lamb,
sheep, wild sheep, and domestic sheep.

@@

\begin{Shaded}
\begin{Highlighting}[]
\ConstantTok{ENV}\NormalTok{[}\StringTok{"NCBITAXONOMY\_PATH"}\NormalTok{] }\OperatorTok{=}\NormalTok{ joinpath(homedir()}\OperatorTok{,} \StringTok{"data"}\OperatorTok{,} \StringTok{"NCBITaxonomy.jl"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{using}\NormalTok{ Pkg}
\NormalTok{Pkg.add(}\StringTok{"NCBITaxonomy"}\NormalTok{) }\CommentTok{\# Dowloading the files may take a long time}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{julia}\OperatorTok{\textgreater{}}\NormalTok{ similarnames(}\StringTok{"Adeno{-}associated virus 3b"}\OperatorTok{;}\NormalTok{ threshold}\OperatorTok{=}\FloatTok{0.95}\NormalTok{)}
\FloatTok{3}\OperatorTok{{-}}\NormalTok{element }\DataTypeTok{Vector}\NormalTok{\{}\DataTypeTok{Pair}\NormalTok{\{NCBITaxon}\OperatorTok{,} \DataTypeTok{Float64}\NormalTok{\}\}}\OperatorTok{:}
\NormalTok{  Adeno}\OperatorTok{{-}}\NormalTok{associated virus }\OperatorTok{{-}} \FloatTok{3}\NormalTok{ (ncbi}\OperatorTok{:}\FloatTok{46350}\NormalTok{) }\OperatorTok{=\textgreater{}} \FloatTok{0.96}
\NormalTok{   Adeno}\OperatorTok{{-}}\NormalTok{associated virus }\FloatTok{3}\NormalTok{B (ncbi}\OperatorTok{:}\FloatTok{68742}\NormalTok{) }\OperatorTok{=\textgreater{}} \FloatTok{0.96}
\NormalTok{ Adeno}\OperatorTok{{-}}\NormalTok{associated virus }\FloatTok{3}\NormalTok{A (ncbi}\OperatorTok{:}\FloatTok{1406223}\NormalTok{) }\OperatorTok{=\textgreater{}} \FloatTok{0.96}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{julia}\OperatorTok{\textgreater{}}\NormalTok{ taxon(}\StringTok{"Adeno{-}associated virus 3b"}\OperatorTok{;}\NormalTok{ casesensitive}\OperatorTok{=}\ExtensionTok{false}\NormalTok{)}
\NormalTok{Adeno}\OperatorTok{{-}}\NormalTok{associated virus }\FloatTok{3}\NormalTok{B (ncbi}\OperatorTok{:}\FloatTok{68742}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{try}
\NormalTok{  taxon(name)}
  \CommentTok{\# Additional operations with the matched name}
\KeywordTok{catch}\NormalTok{ err}
  \KeywordTok{if}\NormalTok{ isa(err}\OperatorTok{,}\NormalTok{ NameHasNoDirectMatch)}
    \CommentTok{\# What to do if no match is found}
  \KeywordTok{elseif}\NormalTok{ isa(err}\OperatorTok{,}\NormalTok{ NameHasMultipleMatches)}
    \CommentTok{\# What to do if there are multiple matches}
  \KeywordTok{else}
    \CommentTok{\# What to do in case of another error that is not NCBITaxonomy specific}
  \KeywordTok{end}
\KeywordTok{end}
\end{Highlighting}
\end{Shaded}

@@

\begin{longtable}[]{@{}lclll@{}}
\toprule
Names list & Fuzzy matching & Time (ms) & Allocations & Memory
allocated\tabularnewline
\midrule
\endhead
all & no & 23 & 34 & 2 KiB\tabularnewline
& yes & 105 & 2580 & 25 MiB\tabularnewline
\texttt{mammalfilter(true)} & no & 0.55 & 32 & 2 KiB\tabularnewline
& yes & 1.9 & 551 & 286 KiB\tabularnewline
\texttt{primatefilter()} & no & 0.15 & 33 & 2 KiB\tabularnewline
& yes & 0.3 & 92 & 27 KiB\tabularnewline
\bottomrule
\end{longtable}

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-Barchard2011PreHum}{}%
Barchard, K. and Pace, L. 2011. Preventing human error: The impact of
data entry methods on data accuracy and statistical results. - Computers
in Human Behavior 27: 1834--1839.

\leavevmode\hypertarget{ref-Bezanson2017JulFre}{}%
Bezanson, J. et al. 2017. Julia: A Fresh Approach to Numerical
Computing. - SIAM Review 59: 65--98.

\leavevmode\hypertarget{ref-Carlson2022GloVir}{}%
Carlson, C. J. et al. 2022. The Global Virome in One Network (VIRION):
An Atlas of Vertebrate-Virus Associations. - mBio in press.

\leavevmode\hypertarget{ref-Chamberlain2013TaxTax}{}%
Chamberlain, S. A. and Szöcs, E. 2013. Taxize: Taxonomic search and
retrieval in R. - F1000Research 2: 191.

\leavevmode\hypertarget{ref-Conti2021MatAlg}{}%
Conti, M. et al. 2021. Match Algorithms for Scientific Names in
FlorItaly, the Portal to the Flora of Italy. - Plants 10: 974.

\leavevmode\hypertarget{ref-Dauncey2016ComMis}{}%
Dauncey, E. A. et al. 2016. Common mistakes when using plant names and
how to avoid them. - European Journal of Integrative Medicine 8:
597--601.

\leavevmode\hypertarget{ref-Dikow2009BioRes}{}%
Dikow, T. et al. 2009. Biodiversity Research Based on Taxonomic
Revisions - A Tale of Unrealized Opportunities. - In: Diptera Diversity:
Status, Challenges and Tools. Brill, pp. 323--346.

\leavevmode\hypertarget{ref-Federhen2012NcbTax}{}%
Federhen, S. 2012. The NCBI taxonomy database. - Nucleic acids research
40: D136--D143.

\leavevmode\hypertarget{ref-Gibb2021DatPro}{}%
Gibb, R. et al. 2021. Data Proliferation, Reconciliation, and Synthesis
in Viral Ecology. - BioScience in press.

\leavevmode\hypertarget{ref-Lefkowitz2018VirTax}{}%
Lefkowitz, E. J. et al. 2018. Virus taxonomy: The database of the
International Committee on Taxonomy of Viruses (ICTV). - Nucleic Acids
Research 46: D708--D717.

\leavevmode\hypertarget{ref-Melville2021RetApp}{}%
Melville, J. et al. 2021. A return-on-investment approach for
prioritization of rigorous taxonomic research needed to inform responses
to the biodiversity crisis. - PLOS Biology 19: e3001210.

\leavevmode\hypertarget{ref-Norman2020TaxHig}{}%
Norman, K. E. A. et al. 2020. Taxadb: A high-performance local taxonomic
database interface. - Methods in Ecology and Evolution 11: 1153--1159.

\leavevmode\hypertarget{ref-Schoch2020NcbTax}{}%
Schoch, C. L. et al. 2020. NCBI Taxonomy: A comprehensive update on
curation, resources and tools. - Database in press.

\leavevmode\hypertarget{ref-Shimatani2001MeaSpe}{}%
Shimatani, K. 2001. On the Measurement of Species Diversity
Incorporating Species Differences. - Oikos 93: 135--147.

\leavevmode\hypertarget{ref-Wagner2016RevSof}{}%
Wagner, V. 2016. A review of software tools for spell-checking taxon
names in vegetation databases. - Journal of Vegetation Science 27:
1323--1327.

\leavevmode\hypertarget{ref-Walker2020ChaVir}{}%
Walker, P. J. et al. 2020. Changes to virus taxonomy and the Statutes
ratified by the International Committee on Taxonomy of Viruses (2020). -
Archives of Virology 165: 2737--2748.

>>>>

\usepackage{gensymb}

@@

\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc} % for \widthof, \maxof
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\maxof{\widthof{#1}}{\csllabelwidth}}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth}{#1}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}\geometry{verbose,letterpaper,tmargin=2.2cm,bmargin=2.2cm,lmargin=2.2cm,rmargin=2.2cm}

@@

%
\href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
%
\,\textsuperscript{1,2}\quad %
\href{https://orcid.org/0000-0002-0965-1649}{Rory\,Gibb}%
%
\,\textsuperscript{3,4,5}\quad %
\href{https://orcid.org/0000-0002-4308-6321}{Sadie J.\,Ryan}%
%
\,\textsuperscript{6,7,8}\quad %
\href{https://orcid.org/0000-0001-6960-8434}{Colin J.\,Carlson}%
%
\,\textsuperscript{10,9}

\textsuperscript{1}\,Université de Montréal, Départment de Sciences
Biologiques, Montréal QC, Canada\quad \textsuperscript{10}\,Center for
Global Health Science and Security, Georgetown University Medical
Center, Georgetown University, Washington, D.C., United States of
America\quad \textsuperscript{2}\,Québec Centre for Biodiversity
Science, Montréal, QC, Canada\quad \textsuperscript{3}\,Centre on
Climate Change and Planetary Health, London School of Hygiene and
Tropical Medicine, London, UK\quad \textsuperscript{4}\,Centre for
Mathematical Modelling of Infectious Diseases, London School of Hygiene
and Tropical Medicine, London, UK\quad \textsuperscript{5}\,Current
address: Centre for Biodiversity and Environment Research, University
College London, London, UK\quad \textsuperscript{6}\,Emerging Pathogens
Institute, University of Florida, Gainesville, FL, United States of
America\quad \textsuperscript{7}\,School of Life Sciences, University of
KwaZulu-Natal, Durban, South Africa\quad \textsuperscript{8}\,Department
of Geography, University of Florida, Gainesville, FL, United States of
America\quad \textsuperscript{9}\,Department of Microbiology and
Immunology, Georgetown University Medical Center, Georgetown University,
Washington, D.C., United States of America

@@

\texttt{NCBITaxonomy.jl} is a package designed to facilitate the
reconciliation and cleaning of taxonomic names, using a local copy of
the NCBI taxonomic backbone (Federhen 2012, Schoch et al. 2020); The
basic search functions are coupled with quality-of-life functions
including case-insensitive search and custom fuzzy string matching to
facilitate the amount of information that can be extracted automatically
while allowing efficient manual curation and inspection of results.
\texttt{NCBITaxonomy.jl} works with version 1.6 of the Julia programming
language (Bezanson et al. 2017), and relies on the Apache Arrow format
to store a local copy of the NCBI raw taxonomy files. The design of
\texttt{NCBITaxonomy.jl} has been inspired by similar efforts, like the
R package \texttt{taxadb} (Norman et al. 2020), which provides an
offline alternative to packages like \texttt{taxize} (Chamberlain and
Szöcs 2013).

@@

@@

Unambiguously identifying species is a far more challenging task than it
may appear. There are a vast number of reasons for this. Different
databases keep different taxonomic ``backbones'', \emph{i.e.} different
data structures in which names are mapped to species, and organised in a
hierarchy. Not all names are unique identifiers to groups. For example,
\emph{Io} can either refer to a genus of plants from the aster family,
or to a genus of molluscs; the genus \emph{Mus} (of which the house
mouse \emph{Mus musculus} is a species), contains a sub-genus
\emph{also} named \emph{Mus} (within which \emph{Mus musculus} is
located). Conversely, the same species can have several names, which are
valid synonyms: for example, the domestic cow \emph{Bos taurus} admits
\emph{Bos primigenius taurus} as a valid synonym. In addition to
binomial names, the same species can be known by many vernacular
(common) names, which are language or even region-specific: \emph{Ovis
aries}, for example, has valid English vernaculars including lamb,
sheep, wild sheep, and domestic sheep.

@@

\begin{Shaded}
\begin{Highlighting}[]
\ConstantTok{ENV}\NormalTok{[}\StringTok{"NCBITAXONOMY\_PATH"}\NormalTok{] }\OperatorTok{=} \FunctionTok{joinpath}\NormalTok{(}\FunctionTok{homedir}\NormalTok{(), }\StringTok{"data"}\NormalTok{, }\StringTok{"NCBITaxonomy.jl"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\ImportTok{using} \BuiltInTok{Pkg}
\BuiltInTok{Pkg}\NormalTok{.}\FunctionTok{add}\NormalTok{(}\StringTok{"NCBITaxonomy"}\NormalTok{) }\CommentTok{\# Dowloading the files may take a long time}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{julia}\OperatorTok{\textgreater{}} \FunctionTok{similarnames}\NormalTok{(}\StringTok{"Adeno{-}associated virus 3b"}\NormalTok{; threshold}\OperatorTok{=}\FloatTok{0.95}\NormalTok{)}
\FloatTok{3}\OperatorTok{{-}}\NormalTok{element }\DataTypeTok{Vector}\NormalTok{\{}\DataTypeTok{Pair}\NormalTok{\{NCBITaxon, }\DataTypeTok{Float64}\NormalTok{\}\}}\OperatorTok{:}
\NormalTok{  Adeno}\OperatorTok{{-}}\NormalTok{associated virus }\OperatorTok{{-}} \FloatTok{3}\NormalTok{ (ncbi}\OperatorTok{:}\FloatTok{46350}\NormalTok{) }\OperatorTok{=\textgreater{}} \FloatTok{0.96}
\NormalTok{   Adeno}\OperatorTok{{-}}\NormalTok{associated virus }\FloatTok{3}\NormalTok{B (ncbi}\OperatorTok{:}\FloatTok{68742}\NormalTok{) }\OperatorTok{=\textgreater{}} \FloatTok{0.96}
\NormalTok{ Adeno}\OperatorTok{{-}}\NormalTok{associated virus }\FloatTok{3}\NormalTok{A (ncbi}\OperatorTok{:}\FloatTok{1406223}\NormalTok{) }\OperatorTok{=\textgreater{}} \FloatTok{0.96}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{julia}\OperatorTok{\textgreater{}} \FunctionTok{taxon}\NormalTok{(}\StringTok{"Adeno{-}associated virus 3b"}\NormalTok{; casesensitive}\OperatorTok{=}\ConstantTok{false}\NormalTok{)}
\NormalTok{Adeno}\OperatorTok{{-}}\NormalTok{associated virus }\FloatTok{3}\NormalTok{B (ncbi}\OperatorTok{:}\FloatTok{68742}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{try}
  \FunctionTok{taxon}\NormalTok{(name)}
  \CommentTok{\# Additional operations with the matched name}
\NormalTok{catch err}
  \ControlFlowTok{if} \FunctionTok{isa}\NormalTok{(err, NameHasNoDirectMatch)}
    \CommentTok{\# What to do if no match is found}
  \ControlFlowTok{elseif} \FunctionTok{isa}\NormalTok{(err, NameHasMultipleMatches)}
    \CommentTok{\# What to do if there are multiple matches}
  \ControlFlowTok{else}
    \CommentTok{\# What to do in case of another error that is not NCBITaxonomy specific}
  \ControlFlowTok{end}
\KeywordTok{end}
\end{Highlighting}
\end{Shaded}

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2857}}
  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1286}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1571}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2286}}@{}}
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
Names list
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Fuzzy matching
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Time (ms)
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Allocations
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Memory allocated
\end{minipage} \\
\midrule()
\endhead
all & no & 23 & 34 & 2 KiB \\
& yes & 105 & 2580 & 25 MiB \\
\texttt{mammalfilter(true)} & no & 0.55 & 32 & 2 KiB \\
& yes & 1.9 & 551 & 286 KiB \\
\texttt{primatefilter()} & no & 0.15 & 33 & 2 KiB \\
& yes & 0.3 & 92 & 27 KiB \\
\bottomrule()
\end{longtable}

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-Barchard2011PreHum}{}}%
Barchard, K. and Pace, L. 2011.
\href{https://doi.org/10.1016/j.chb.2011.04.004}{Preventing human error:
The impact of data entry methods on data accuracy and statistical
results}. - Computers in Human Behavior 27: 1834--1839.

\leavevmode\vadjust pre{\hypertarget{ref-Bezanson2017JulFre}{}}%
Bezanson, J. et al. 2017.
\href{https://doi.org/10.1137/141000671}{Julia: A Fresh Approach to
Numerical Computing}. - SIAM Review 59: 65--98.

\leavevmode\vadjust pre{\hypertarget{ref-Carlson2022GloVir}{}}%
Carlson, C. J. et al. 2022.
\href{https://doi.org/10.1128/mbio.02985-21}{The Global Virome in One
Network (VIRION): An Atlas of Vertebrate-Virus Associations}. - mBio in
press.

\leavevmode\vadjust pre{\hypertarget{ref-Chamberlain2013TaxTax}{}}%
Chamberlain, S. A. and Szöcs, E. 2013.
\href{https://doi.org/10.12688/f1000research.2-191.v2}{Taxize: Taxonomic
search and retrieval in R}. - F1000Research 2: 191.

\leavevmode\vadjust pre{\hypertarget{ref-Conti2021MatAlg}{}}%
Conti, M. et al. 2021. Match Algorithms for Scientific Names in
FlorItaly, the Portal to the Flora of Italy. - Plants 10: 974.

\leavevmode\vadjust pre{\hypertarget{ref-Dauncey2016ComMis}{}}%
Dauncey, E. A. et al. 2016. Common mistakes when using plant names and
how to avoid them. - European Journal of Integrative Medicine 8:
597--601.

\leavevmode\vadjust pre{\hypertarget{ref-Dikow2009BioRes}{}}%
Dikow, T. et al. 2009. Biodiversity Research Based on Taxonomic
Revisions - A Tale of Unrealized Opportunities. - In: Diptera Diversity:
Status, Challenges and Tools. Brill, pp. 323--346.

\leavevmode\vadjust pre{\hypertarget{ref-Federhen2012NcbTax}{}}%
Federhen, S. 2012. The NCBI taxonomy database. - Nucleic acids research
40: D136--D143.

\leavevmode\vadjust pre{\hypertarget{ref-Gibb2021DatPro}{}}%
Gibb, R. et al. 2021. \href{https://doi.org/10.1093/biosci/biab080}{Data
Proliferation, Reconciliation, and Synthesis in Viral Ecology}. -
BioScience in press.

\leavevmode\vadjust pre{\hypertarget{ref-Lefkowitz2018VirTax}{}}%
Lefkowitz, E. J. et al. 2018.
\href{https://doi.org/10.1093/nar/gkx932}{Virus taxonomy: The database
of the International Committee on Taxonomy of Viruses (ICTV)}. - Nucleic
Acids Research 46: D708--D717.

\leavevmode\vadjust pre{\hypertarget{ref-Melville2021RetApp}{}}%
Melville, J. et al. 2021.
\href{https://doi.org/10.1371/journal.pbio.3001210}{A
return-on-investment approach for prioritization of rigorous taxonomic
research needed to inform responses to the biodiversity crisis}. - PLOS
Biology 19: e3001210.

\leavevmode\vadjust pre{\hypertarget{ref-Norman2020TaxHig}{}}%
Norman, K. E. A. et al. 2020.
\href{https://doi.org/10.1111/2041-210X.13440}{Taxadb: A
high-performance local taxonomic database interface}. - Methods in
Ecology and Evolution 11: 1153--1159.

\leavevmode\vadjust pre{\hypertarget{ref-Schoch2020NcbTax}{}}%
Schoch, C. L. et al. 2020. NCBI Taxonomy: A comprehensive update on
curation, resources and tools. - Database in press.

\leavevmode\vadjust pre{\hypertarget{ref-Shimatani2001MeaSpe}{}}%
Shimatani, K. 2001. \href{https://www.jstor.org/stable/3547217}{On the
Measurement of Species Diversity Incorporating Species Differences}. -
Oikos 93: 135--147.

\leavevmode\vadjust pre{\hypertarget{ref-Wagner2016RevSof}{}}%
Wagner, V. 2016. A review of software tools for spell-checking taxon
names in vegetation databases. - Journal of Vegetation Science 27:
1323--1327.

\leavevmode\vadjust pre{\hypertarget{ref-Walker2020ChaVir}{}}%
Walker, P. J. et al. 2020.
\href{https://doi.org/10.1007/s00705-020-04752-x}{Changes to virus
taxonomy and the Statutes ratified by the International Committee on
Taxonomy of Viruses (2020)}. - Archives of Virology 165: 2737--2748.
